High-Dimensional Regularized Discriminant Analysis

### 2013-04-26 reports/paper-rda.Rnw
Applied final edits from DMY. Also, changed figures to black and white.

\usepackage{graphicx, amsmath, amssymb, bm, natbib}
\newcommand{\xbar}{\bar{x}}
\newcommand{\tr}{\text{tr}}
\DeclareMathOperator*{\argmin}{arg\,min}

\newtheorem{cor}{Corollary}
%\newtheorem{lemma}{Lemma}
%\newtheorem{proposition}{Proposition}
\newtheorem{thm}{Theorem}

@@

@@

A reliable supervised classification of tumors from gene expression microarray
data is essential for successful diagnosis and treatment of diseases such as
cancer; however, the analysis of microarray data often presents difficult
challenges because the number of gene expression levels is typically much
greater than the sample size. Consequently, several sparse and regularized
classifiers have been proposed, often with strict covariance assumptions or
eigenvalue adjustments to ensure that the classifiers are well-posed. Here, we
propose a novel modification of the regularized discriminant analysis classifier
popularized by \cite{Friedman:1989tm}. Our proposed classifier provides a
straightforward interpretation and employs a new dimension-reduction technique
to enable a computationally efficient model-selection procedure, thus overcoming
the computational shortcomings of \citeauthor{Friedman:1989tm}'s classifier for
high-dimensional data. Moreover, we demonstrate with several high-dimensional
microarray data sets that our proposed classifier is competitive and often
superior to several recently proposed sparse and regularized classifiers in
terms of classification accuracy. Finally, we provide an implementation of our
proposed classifier in the {\tt sparsediscrim} R package, available on CRAN.

@@

In this paper we modify \citeauthor{Friedman:1989tm}'s classifier by first
constructing the pooling matrix as a convex combination of the covariance-matrix
estimators employed in linear and quadratic discriminant analysis and
demonstrate that this simplification improves the interpretation of the pooling
operation of \citeauthor{Friedman:1989tm}'s classifier. Given that the
assumption of equal population covariance matrices within linear discriminant
analysis is often too stringent in practice \citep{Clemmensen:2011kr}, our
proposed classifier can relax the linearity assumption by instead incorporating
unequal covariance matrices while retaining linear and quadratic discriminant
analysis as special cases. We then establish our classifier by applying
covariance-matrix regularization with a parameterization that includes a large
family of shrinkage methods, such as those from \cite{Srivastava:2007ww},
\cite{Rao:1971ul}, and other methods studied by \cite{Ramey:2013ji} and
\cite{Xu:2009fl}.

@@

We also demonstrate that our proposed classifier is competitive with and often
superior to several recent classifiers designed for small-sample,
high-dimensional data. In particular, we compare our classifier with diagonal
linear discriminant analysis from \cite{Dudoit:2002ev} and the recently proposed
classifiers from \cite{Guo:2007te}, \cite{Pang:2009ik}, \cite{Tong:2012hw}, and
\cite{Witten:2011kc}. We conduct our comparison of the classification accuracy
of the competing classifiers using four small-sample, high-dimensional
benchmark microarray data sets.

@@

Throughout the document we also require the following additional notation. Let
$I_m$ be the $m \times m$ identity matrix, and let $0_{m \times p}$ be
the $m \times p$ matrix of zeros, such that $0_m$ is understood to denote
$0_{m \times m}$. Lastly, for $c \in \mathbb{R}$, let $c^+ = 1/c$ if $c \ne
0$ and $0$ otherwise. Let $A \oplus B$ denote the direct sum of $A \in
\mathbb{R}_{r \times r}$ and $B \in \mathbb{R}_{s \times s}$ \citep[Chapter
  1]{Lutkepohl:1996uz}. Let $A^+$ and $\mathcal{N}(A) = \{z \in \mathbb{R}_{p
  \times 1} : A z = 0_{m \times 1}\}$ denote the Moore-Penrose pseudoinverse and null space
of $A \in \mathbb{R}_{m \times p}$, respectively. Let $V^{\perp} = \{y
\in \mathbb{R}_{p \times 1} : y^{T}v = 0\ \forall v \in V \}$ denote
the orthogonal complement of a vector space $V \subset \mathbb{R}_{p \times 1}$.

@@

\[ \left[\text{Figure \ref{fig:hdrda-contours} goes about here }\right]\]

@@

\begin{lemma}\label{lemma:rda-tilde-Sigma_k}
Let $\widehat{\Sigma} = U D U^{T}$ be the eigendecomposition of
$\widehat{\Sigma}$ as above, and suppose that rank$(\widehat{\Sigma}) =
q \le p$. Then, we have
\begin{align}
	\tilde{\Sigma}_k &= U(W_k \oplus \gamma I_{p-q})U^{T} \quad
  (k = 1, \ldots, K),\label{eq:rda-matrix}
\intertext{where}
W_k &= \alpha_k \{(1 - \lambda) U_1^{T} \widehat{\Sigma}_k U_1 + \lambda D_q\} + \gamma I_{q}.\label{eq:Wk}
\end{align}
\end{lemma}
\begin{proof}
From Lemma \ref{lemma:null-spaces}, the columns of $U_2$ span the null space
of $\widehat{\Sigma}$, which implies that $\widehat{\Sigma}_k U_2 =
0_{p \times (p - q)}$. Hence, $U^{T} \widehat{\Sigma}_k U = 
U_1^{T} \widehat{\Sigma}_k U_1 \oplus 0_{p-q}$ $(k = 1, \ldots,
K)$. Thus, $U^{T} \tilde{\Sigma}_k U = \alpha_k \{(1 - \lambda) U^{T}
\widehat{\Sigma}_k U + \lambda D\} + \gamma I_p$, and
\eqref{eq:rda-matrix} follows because $U$ is orthogonal.
\end{proof}

@@

Thus far, we have constructed each $\tilde{\Sigma}_k$ in terms of the first $q$
eigenvectors of $\widehat{\Sigma}$. By utilizing a technique similar to the
so-called kernel trick, we can obtain $U_1$ by computing the eigendecomposition
of a much smaller $N \times N$ matrix when $p \gg N$
\citep{Hastie:2008dt}. Recall that the pooled sample covariance matrix
$\widehat{\Sigma} = X^{T} X$. Then, because $X = M D^{1/2} U^{T}$ by the
singular value decomposition, we have the eigendecomposition $\widehat{\Sigma} =
U D U^{T}$, where $M \in \mathbb{R}_{N \times N}$ is orthogonal, $D^{1/2} \in
\mathbb{R}_{N \times N}^{\ge}$ is a diagonal matrix consisting of the singular
values of $X$, and $U \in \mathbb{R}_{p \times N}$ is orthogonal. Now, $X X^{T}
= M D M^{T}$ is the eigenvalue decomposition of $X X^{T}$, where $D$ is the
matrix of eigenvalues of $X X^{T}$ and the columns of $M$ are the corresponding
eigenvectors. Hence, we obtain $M$ and $D$ from an eigendecomposition of $X
X^{T} \in \mathbb{R}_{N \times N}$. Next, we compute $U = X^{T} M D^{+/2}$,
where $D^{+/2} = D_q^{-1/2} \oplus 0_{N-q}$. We then determine $q$ by computing
the number of numerically nonzero eigenvalues present in $D$, where $q$ is the
number of eigenvalues that exceeds some tolerance value, say, $\epsilon = 1
\times 10^{-6}$. After calculating $q$, we extract $U_1$ by retaining only the
first $q$ columns of $U$.

\section{High-Dimensional Microarray Data Sets}

@@

We used version 3.0.0 of the open-source statistical software {\tt R} for the
classification study. We used the implementations of the Witten and Guo
classifiers from the {\tt penalizedLDA} and {\tt rda} packages, respectively, on
CRAN. Because the {\tt rda} package does not perform the authors' ``Min-Min''
rule automatically, we applied this rule in our {\tt R} code. We also utilized
our implementations of the Dudoit, Pang, and Tong classifiers available in the
{\tt sparsediscrim} package. We used the default settings for each classifier
with the exception that we explicitly set prior probabilities as equal, if the
option was available. For our classifier, we set $\alpha_k = 1$ $(k = 1, \ldots,
K)$, so that the covariance-matrix estimator \eqref{eq:hdrda-cov} employed had a
form resembling \eqref{eq:ridge-estimator}. We estimated $\lambda$ from a grid
of 21 equidistant candidate values between 0 and 1, inclusively. Similarly, we
estimated $\gamma$ from a grid consisting of the values $10^{-1}, \ldots, 10^4$,
and $10^5$. We selected optimal estimates of $\lambda$ and $\gamma$ using
10-fold cross-validation \citep{Hastie:2008dt}.

@@

Our classifier was superior in classification performance for the majority of
the simulations. For the Burczysnki, Shipp, and Singh data sets, our classifier
outperformed its competitors for all values of $d$ examined. For the Nakayama
data set, our classifier was outperformed by the Dudoit, Pang, and Tong
classifiers for small values of $d$ but attained classification rates superior
to its competitors for larger values of $d$. Furthermore, Figure
\ref{fig:error-rates} emphasizes two strengths of our classifier: reliability of
the classifier for small $d$ and stability of the classifier for large $d$. In
contrast to the other classifiers, our classifier exhibited less variability in
its misclassification estimates for small values of $d$. Also, our classifier
yielded superior classification accuracy as $d$ increased and was hardly
effected by the inclusion of more variables in the data sets. We attribute the
apparent stability of the error-rate estimates of our classifier for large
values of $d$ to its novel dimension-reduction technique.

@@

The classification performance of the the Dudoit, Pang, Tong, and Witten
classifiers for the Shipp and Singh data sets revealed the inability of these
methods to handle larger values of $d$. After closer examination of the
classification studies performed in the authors' original papers, we noticed
that classification accuracy estimates were reported only for small values of
$d$, thereby ignoring the inclusion of a larger number of variables. Hence, we
advise that practioners be aware of the necessity to filter a large number of
features before employing these methods, lest their classification performance
can degrade.

The popular Guo classifier is most competitive over large values of $d$ for the
Shipp and Singh data sets. However, for the Burczynski and Nakayama data sets,
the implementation of the Guo method in the {\tt rda} package often classified
every test observation into a single class, thus yielding larger error rates
than its competitors. Furthermore, the Guo classifier exhibited unreliable
classification performance for smaller values of $d$. The Guo classifier
required a larger subset of the features to perform competitively in our study.
\[ \left[\text{Figure \ref{fig:error-rates} goes about here }\right]\]
Next, we examine the optimal estimates of the tuning parameters for our
classifier. For brevity, we provide graphical summaries of the optimal estimates
of $\lambda$ and $\gamma$ in the Supplementary Material. For each of the four
data sets, the distribution of the optimal values of $\lambda$ selected through
cross-validation often had a notable bathtub shape, resembling a Beta
distribution with both shape parameters less than unity. Specifically, the
optimal values of $\lambda$ were typically near 0 or near 1, corresponding to
quadratic and linear discriminant analysis, respectively. For instance, with
smaller values of $d$ applied to the Shipp data set, the range of optimal values
of $\lambda$ was typically no larger than 0.05, indicating there were a large
number of training data sets for which we can safely assume the covariance
matrices are unequal or nearly unequal. As $d$ increased, the majority of the
optimal values of $\lambda$ were selected as unity, thereby an increased number
of variables resulted in our classifier preferring the more parsimonious
assumption of equal covariance matrices. In this instance we can see the
flexibility of our classifier to employ the more realistic assumption that the
class covariance matrices are unequal, but if optimal, we can employ the more
parsimonious assumption of equal covariance matrices.

@@

\clearpage

\begin{figure}
<<hdrda_contours, fig.width=8, fig.height=8, out.width='.49\\linewidth', fig.show='hold'>>=
rda_contours(lambda = 0)
rda_contours(lambda = 1/4)
rda_contours(lambda = 3/4)
rda_contours(lambda = 1)
@ 
\caption{Contours of five multivariate normal populations as a function of the
  pooling parameter $\lambda$.}
\label{fig:hdrda-contours}
\end{figure}

\begin{figure}
<<error_rates>>=
error_rates$data_set <- Hmisc:::capitalize(error_rates$data_set)
p <- ggplot(error_rates, aes(x = d, y = Avg_Error, group = Classifier))
p <- p + geom_line(aes(color = Classifier), size = 1.5, linetype = 2)
p <- p + geom_point(aes(color = Classifier, shape = Classifier), size = 4)
p <- p + facet_wrap(~ data_set) + ylim(c(0, max(error_rates$Avg_Error))) + theme_bw()
p <- p + xlab("Number of Variables Selected, d") + ylab("Average Error Rate")
p <- p + theme(axis.text = element_text(size = 16))
p <- p + theme(axis.title.x = element_text(size = 20))
p <- p + theme(axis.title.y = element_text(size = 20))
p <- p + theme(strip.text.x = element_text(size = 18))
p + theme(legend.position = "none")
@ 
\caption{Averages of the 1000 error-rate estimates of the competing classifiers
  for each data set as a function of $d$. The classifiers are marked as follows:
  Dudoit (red circle), Guo (gold triangle), Pang (green square), Tong = (cyan
  cross), Witten (blue square with X), and ours (pink asterisk). Approximate
  standard errors are no greater than $\Sexpr{gsub('.', '\\cdot', round(max_se, 3), fixed = TRUE)}$.}
\label{fig:error-rates}
\end{figure}

>>>>

\usepackage{graphicx, amsmath, amssymb, bm, natbib}

\newtheorem{cor}{Corollary}
\newtheorem{thm}{Theorem}

@@

\newcommand{\xbar}{\bar{x}}
\newcommand{\tr}{\text{tr}}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

A reliable supervised classification of tumors from gene expression microarray
data is essential for successful diagnosis and treatment of diseases such as
cancer; however, the analysis of microarray data often presents difficult
challenges because the number of gene expression levels is typically much
greater than the sample size. Consequently, several sparse and regularized
classifiers have been proposed, often with strict covariance assumptions or
eigenvalue adjustments to ensure that the classifiers are well-posed. Here, we
propose a novel modification of the regularized discriminant analysis classifier
popularized by \cite{Friedman:1989tm}. Our proposed classifier provides a
straightforward interpretation and employs a new dimension-reduction technique
to enable a computationally efficient model-selection procedure, thus overcoming
the computational shortcomings of \citeauthor{Friedman:1989tm}'s classifier for
high-dimensional data. Moreover, we demonstrate with four high-dimensional
microarray data sets that our proposed classifier is competitive with and often
superior to several recently proposed sparse and regularized classifiers in
terms of classification accuracy. Finally, we provide an implementation of our
proposed classifier in the {\tt sparsediscrim} R package, available on CRAN.

@@

In this paper we modify \citeauthor{Friedman:1989tm}'s classifier by first
constructing the pooling matrix as a convex combination of the covariance-matrix
estimators employed in linear and quadratic discriminant analysis and
demonstrate that this simplification improves the interpretation of the pooling
operation of \citeauthor{Friedman:1989tm}'s classifier. Given that the
assumption of equal population covariance matrices for linear discriminant
analysis is often too stringent in practice \citep{Clemmensen:2011kr}, our
proposed classifier can relax the linearity assumption by instead incorporating
unequal covariance matrices while retaining linear and quadratic discriminant
analysis as special cases. We then establish our classifier by applying
covariance-matrix regularization with a parameterization that includes a large
family of shrinkage methods, such as those from \cite{Srivastava:2007ww},
\cite{Rao:1971ul}, and other methods studied by \cite{Ramey:2013ji} and
\cite{Xu:2009fl}.

@@

We also demonstrate that our proposed classifier is competitive with and often
superior to several recent classifiers designed for small-sample,
high-dimensional data. In particular, we compare our classifier with diagonal
linear discriminant analysis proposed by \cite{Dudoit:2002ev} and the recently
proposed classifiers from \cite{Guo:2007te}, \cite{Pang:2009ik},
\cite{Tong:2012hw}, and \cite{Witten:2011kc}. We conduct our comparison of the
classification accuracy of the competing classifiers using four small-sample,
high-dimensional benchmark microarray data sets.

@@

Throughout the document we also require the following additional notation. Let
$I_m$ be the $m \times m$ identity matrix, and let $0_{m \times p}$ be the $m
\times p$ matrix of zeros, such that $0_m$ is understood to denote $0_{m \times
  m}$. For $c \in \mathbb{R}$, let $c^+ = 1/c$ if $c \ne 0$ and $0$
otherwise. Let $A \oplus B$ denote the direct sum of $A \in \mathbb{R}_{r \times
  r}$ and $B \in \mathbb{R}_{s \times s}$ \citep[Chapter
  1]{Lutkepohl:1996uz}. Let $A^+$ and $\mathcal{N}(A) = \{z \in \mathbb{R}_{p
  \times 1} : A z = 0_{m \times 1}\}$ denote the Moore-Penrose pseudoinverse and
null space of $A \in \mathbb{R}_{m \times p}$, respectively. Let $V^{\perp} =
\{y \in \mathbb{R}_{p \times 1} : y^{T}v = 0\ \forall v \in V \}$ denote the
orthogonal complement of a vector space $V \subset \mathbb{R}_{p \times 1}$.

@@

\begin{figure}
<<hdrda_contours, fig.width=8, fig.height=8, out.width='.49\\linewidth', fig.show='hold'>>=
rda_contours(lambda = 0)
rda_contours(lambda = 1/4)
rda_contours(lambda = 3/4)
rda_contours(lambda = 1)
@ 
\caption{Contours of five multivariate normal populations as a function of the
  pooling parameter $\lambda$.}
\label{fig:hdrda-contours}
\end{figure}

@@

\begin{lemma}\label{lemma:rda-tilde-Sigma_k}
Let $\widehat{\Sigma} = U D U^{T}$ be the eigendecomposition of
$\widehat{\Sigma}$ as above, and suppose that rank$(\widehat{\Sigma}) =
q \le p$. Then, we have
\begin{align}
	\tilde{\Sigma}_k &= U(W_k \oplus \gamma I_{p-q})U^{T} \quad
  (k = 1, \ldots, K),\label{eq:rda-matrix}
\intertext{where}
W_k &= \alpha_k \{(1 - \lambda) U_1^{T} \widehat{\Sigma}_k U_1 + \lambda D_q\} + \gamma I_{q}.\label{eq:Wk}
\end{align}
\end{lemma}
\begin{proof}
From Lemma \ref{lemma:null-spaces}, the columns of $U_2$ span the null space
of $\widehat{\Sigma}$, which implies that $\widehat{\Sigma}_k U_2 =
0_{p \times (p - q)}$. Hence, $U^{T} \widehat{\Sigma}_k U = 
U_1^{T} \widehat{\Sigma}_k U_1 \oplus 0_{p-q}$ $(k = 1, \ldots,
K)$. Thus, $U^{T} \tilde{\Sigma}_k U = \alpha_k \{(1 - \lambda) U^{T}
\widehat{\Sigma}_k U + \lambda D\} + \gamma I_p$, and
\eqref{eq:rda-matrix} holds because $U$ is orthogonal.
\end{proof}

@@

Thus far, we have constructed each $\tilde{\Sigma}_k$ in terms of the first $q$
eigenvectors of $\widehat{\Sigma}$. By utilizing a technique similar to the
so-called kernel trick, we can obtain $U_1$ by computing the eigendecomposition
of a much smaller $N \times N$ matrix when $p \gg N$
\citep{Hastie:2008dt}. Recall that the pooled sample covariance matrix is
$\widehat{\Sigma} = X^{T} X$. Then, because $X = M D^{1/2} U^{T}$ by the
singular value decomposition, we have the eigendecomposition $\widehat{\Sigma} =
U D U^{T}$, where $M \in \mathbb{R}_{N \times N}$ is orthogonal, $D^{1/2} \in
\mathbb{R}_{N \times N}^{\ge}$ is a diagonal matrix consisting of the singular
values of $X$, and $U \in \mathbb{R}_{p \times N}$ is orthogonal. Now, $X X^{T}
= M D M^{T}$ is the eigenvalue decomposition of $X X^{T}$, where $D$ is the
matrix of eigenvalues of $X X^{T}$ and the columns of $M$ are the corresponding
eigenvectors. Hence, we obtain $M$ and $D$ from an eigendecomposition of $X
X^{T} \in \mathbb{R}_{N \times N}$. Next, we compute $U = X^{T} M D^{+/2}$,
where $D^{+/2} = D_q^{-1/2} \oplus 0_{N-q}$. We then determine $q$, the number
of numerically nonzero eigenvalues present in $D$, by calculating the number of
eigenvalues that exceeds some tolerance value, say, $\epsilon = 1 \times
10^{-6}$. After calculating $q$, we extract $U_1$ by retaining only the first
$q$ columns of $U$.

\section{Classification Study}

@@

We used version 3.0.0 of the open-source statistical software {\tt R} for the
classification study. We used the implementations of the Witten and Guo
classifiers from the {\tt penalizedLDA} and {\tt rda} packages, respectively, on
CRAN. Because the {\tt rda} package does not perform the authors' ``Min-Min''
rule automatically, we applied this rule in our {\tt R} code. We also utilized
our implementations of the Dudoit, Pang, and Tong classifiers available in the
{\tt sparsediscrim} package. We used the default settings for each classifier
with the exception that we explicitly set prior probabilities as equal, if the
option was available. For our classifier, we set $\alpha_k = 1$ $(k = 1, \ldots,
K)$, so that the covariance-matrix estimator \eqref{eq:hdrda-cov} employed
resembled \eqref{eq:ridge-estimator}. We estimated $\lambda$ from a grid of 21
equidistant candidate values between 0 and 1, inclusively. Similarly, we
estimated $\gamma$ from a grid consisting of the values $10^{-1}, \ldots, 10^4$,
and $10^5$. We selected optimal estimates of $\lambda$ and $\gamma$ using
10-fold cross-validation \citep{Hastie:2008dt}.

@@

Our classifier was superior in classification performance for the majority of
the simulations. For the Burczysnki, Shipp, and Singh data sets, our classifier
outperformed its competitors for all values of $d$ examined. For the Nakayama
data set, our classifier was outperformed by the Dudoit, Pang, and Tong
classifiers for small values of $d$ but attained classification rates superior
to its competitors for larger values of $d$. Furthermore, Figure
\ref{fig:error-rates} emphasizes two strengths of our classifier: reliability of
the classifier for small $d$ and stability of the classifier for large $d$. In
contrast to the other classifiers, our classifier exhibited less variability in
its misclassification estimates for small values of $d$ and yielded superior
classification accuracy as $d$ increased and was hardly effected by the
inclusion of more variables in the data sets. We attribute the apparent
stability of the error-rate estimates of our classifier for large values of $d$
to its novel dimension-reduction technique.

@@

The classification performance of the the Dudoit, Pang, Tong, and Witten
classifiers for the Shipp and Singh data sets revealed the inability of these
methods to handle larger values of $d$. After closer examination of the
classification studies performed in the authors' original papers, we noticed
that classification accuracy estimates were reported only for small values of
$d$, thereby ignoring the inclusion of a larger number of variables. Hence, we
advise that practioners be aware of the necessity to filter a large number of
features before employing these methods, lest their classification performance
be degraded.

The popular Guo classifier is most competitive over large values of $d$ for the
Shipp and Singh data sets. However, for the Burczynski and Nakayama data sets,
the implementation of the Guo method in the {\tt rda} package often classified
every test observation into a single class, thus yielding larger error rates
than its competitors. Furthermore, the Guo classifier exhibited unreliable
classification performance for smaller values of $d$ and required a larger
subset of the features to perform competitively in our study.
\begin{figure}
<<error_rates>>=
error_rates$data_set <- Hmisc:::capitalize(error_rates$data_set)
p <- ggplot(error_rates, aes(x = d, y = Avg_Error, group = Classifier))
p <- p + geom_line(aes(), size = 1, linetype = 2)
p <- p + geom_point(aes(shape = Classifier), size = 6)
p <- p + facet_wrap(~ data_set) + ylim(c(0, max(error_rates$Avg_Error))) + theme_bw()
p <- p + xlab("Number of Variables Selected, d") + ylab("Average Error Rate")
p <- p + theme(axis.text = element_text(size = 16))
p <- p + theme(axis.title.x = element_text(size = 20))
p <- p + theme(axis.title.y = element_text(size = 20))
p <- p + theme(strip.text.x = element_text(size = 18))
p + theme(legend.position = "none")
@ 
\caption{Averages of the 1000 error-rate estimates of the competing classifiers
  for each data set as a function of $d$. The classifiers are marked as follows:
  Dudoit (circle), Guo (triangle), Pang (square), Tong = (cross), Witten (
  square with X), and ours (asterisk). Approximate standard errors are no
  greater than $\Sexpr{gsub('.', '\\cdot', round(max_se, 3), fixed = TRUE)}$.}
\label{fig:error-rates}
\end{figure}
Next, we examine the optimal estimates of the tuning parameters for our
classifier. For brevity, we provide graphical summaries of the optimal estimates
of $\lambda$ and $\gamma$ in the Supplementary Material. For each of the four
data sets, the distribution of the optimal values of $\lambda$ selected through
cross-validation often had a notable bathtub shape, resembling a Beta
distribution with both shape parameters less than unity. Specifically, the
optimal values of $\lambda$ were typically near 0 or near 1, corresponding to
quadratic and linear discriminant analysis, respectively. For instance, with
smaller values of $d$ applied to the Shipp data set, the range of optimal values
of $\lambda$ was typically no larger than 0.05, indicating there were a large
number of training data sets for which we can safely assume the covariance
matrices are unequal or nearly unequal. As $d$ increased, the majority of the
optimal values of $\lambda$ were selected as unity, thereby an increased number
of variables resulted in our classifier preferring the more parsimonious
assumption of equal covariance matrices. In this instance we can see the
flexibility of our classifier to employ the more realistic assumption that the
class covariance matrices are unequal, but if optimal, we can employ the more
parsimonious assumption of equal covariance matrices.

@@
